Results

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
justification for expl analyses

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure\ \@ref(fig:FigSubjEffort)).
Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
